Per captia consumption

### 2021-06-15 PerCapitaConsumption.Rmd
results from CCA

usersurvey <- c(here("config/mssurvey_spring.R"),
                here("config/mssurvey_fall.R"),
                here("config/mssurvey_spring_01.R"),
                here("config/mssurvey_fall_01.R"))

@@

This is a short run of the CCA model implemented in the latest codebase, so it can produce full age structured output. First we need to process the detailed diet file, and also get the output of `run_truth` for numbers.

@@

@@

>>>>

usersurvey <- c(here("config/mssurvey_spring.R"),
                here("config/mssurvey_fall.R"))

@@

This is a short run of the CCA model implemented in the latest codebase, so it can produce full age structured output. First we need to process the detailed diet file, and also get the output of `run_truth` for numbers. At present it seems the CC model is also producing very low per capita consumpton. This suggests that interpretation of the DetailedDietCheck.txt output is incorrect? It doesn't seem like it is tons consumed at by the population of predators at agecl.

@@

save <- TRUE

@@

# Age structured single species subset
  sppsubset <- fgs %>%
    filter(Name %in% c("Yelloweye_rockfish",
                       "Darkblotched_rockfish",
                       "Bocaccio_rockfish",
                       "Pacific_Ocean_Perch",
                       "Arrowtooth_flounder",
                       "Petrale_sole",
                       "Jack_mackerel",
                       "Pacific_sardine",
                       "Anchovy",
                       "Herring",
                       "Spiny_dogfish")
    )

# Get true data and species subset

CCAtestom <- om_init(here("config/CCConfig_constest.R"))

CCAtestom_ms <- om_species(sppsubset$Name, CCAtestom)

# fall census survey
source(here("config/omdimensions.R"))
source(here("config/mssurvey_CCtest.R"))

omlist_ss <- CCAtestom_ms
